Homicide Increases in the COVID-19 Era

### 2025-02-26 Draft1.qmd
added code used to obtain all but 3,000 ZCTA codes/addresses

@@

@@

>>>>

```{r}
crimes_with_zips <- read.csv("crimes_with_zips.csv") # just inner_join with the crime_la dataset
```

@@

## Data Wrangling {.unnumbered}

# Reading in Raw Datasets

@@

# adding a variable that's just the ZCTA zip code
cali_median_income$ZCTA <- stringr::str_sub(cali_median_income$NAME, -5)

write.csv(cali_median_income, "cali_median_income.csv")
```

### Zip Codes for Crimes {.unnumbered}
```{r, eval=FALSE}
library(sf)
library(dplyr)

crime_la_2010_2019 <- read.csv("Raw_Data/Crime_Data_from_2010_to_2019.csv")

crime_la$DateParsed <- as.POSIXct(crime_la$Date.Rptd, 
                                  format = "%m/%d/%Y %I:%M:%S %p", 
                                  tz = "America/Los_Angeles")

crime_la$year <- as.integer(stringr::str_sub(crime_la$YearWeek, 1, 4))

coords <- crime_la %>% select(LAT, LON, DR_NO, year)

zcta <- read_sf(dsn = "Raw_Data/cb_2020_us_zcta520_500k", layer = "cb_2020_us_zcta520_500k")

  points <- st_as_sf(coords, coords = c("LON", "LAT"), crs = 4326)  # WGS84

  zcta <- st_transform(zcta, 4326)  # Convert ZCTA to WGS84 if needed
  cat("Starting Zip Code Retrieval \n")

  result <- st_join(points, zcta)

  cat("Finished Zip Code Retrieval \n")

  write.csv(result, "crime_zip_files/all_zips.csv")

crime_zctas <- read.csv("Raw_Data/all_zips.csv")
colnames(crime_zctas) <- c(colnames(crime_zctas)[-c(1, length(colnames(crime_zctas)))],"LON", "LAT")

crime_zctas$LON <- as.numeric(gsub('c(', "", crime_zctas$LON, fixed = TRUE))
crime_zctas$LAT <- as.numeric(gsub(')', "", crime_zctas$LAT, fixed = TRUE))
```

```{r}

duplicates <- as.integer(as.character(data.frame(table(crime_zctas$universal_idx)[table(crime_zctas$universal_idx) > 1]) %>% pull(Var1)))

# there are approximately 200 rows that are duplicated (100 incidents) as the area lies on the intersection between two zctas. 
duplicate_data <- crime_zctas %>% filter(universal_idx %in% duplicates)

rev_geo_duplicates <- reverse_geocode(duplicates2, lat = LAT, long = LON)
# the above query identifies the address of these coordinates as KFC, 8644, Balboa Boulevard, Northridge South Neighborhood Council District, Los Angeles, Los Angeles County, California, 91325, United States. 
# therefore, we will only keep the 91325 zip code rows.

crime_zctas_no_duplicates <- crime_zctas %>% mutate(duplicate = ifelse(universal_idx %in% duplicate_data$universal_idx & ZCTA5CE20 != 91325, "Drop", "Keep")) %>% filter(duplicate != "Drop") %>% select(-duplicate)

# it's empty now 
# duplicates <- table(crime_zctas_no_duplicates$universal_idx)[table(crime_zctas_no_duplicates$universal_idx) > 1]

# next, check for NAs
sum(is.na(crime_zctas_no_duplicates$ZCTA5CE20)) # there are 3724 NAs. Let's find them a zip code

# some also have lat long = 0. We'll find those separately
no_zipcode_not0 <- crime_zctas_no_duplicates %>% filter(is.na(ZCTA5CE20) & LON != 0)

no_zipcode_not0_zips <- reverse_geocode(no_zipcode_not0, lat = LAT, long = LON)

no_zipcode_not0_zips$ZCTA5CE20 <- stringr::str_extract(no_zipcode_not0_zips$address, "\\d{5}")

no_zipcode_not0_zips <- no_zipcode_not0_zips %>% select(-address)

crime_zctas2 <- crime_zctas_no_duplicates %>% filter(!is.na(ZCTA5CE20))

crime_zctas3 <- rbind(crime_zctas2, no_zipcode_not0_zips)

crime_zctas4 <- crime_zctas3 %>% filter(!is.na(ZCTA5CE20))

write.csv(crime_zctas4, "crimes_with_zips.csv")

no_zipcode_0s <- crime_zctas_no_duplicates %>% filter(is.na(ZCTA5CE20) & LON == 0) %>% pull(DR_NO)

main_dataset_0s <- crime_la %>% filter(DR_NO %in% no_zipcode_0s)

summary(main_dataset_0s)

summary(crime_la)
```
